---
title: Radiant -- Business analytics using R and Shiny
---

***

Radiant is a tool designed to facilitate decision making using data and models. It is currently used in the Quantitative Analysis and Research for Marketing Decisions classes at the <a href="http://rady.ucsd.edu/" target="\_blank">Rady School of Management</a> by <a href="http://rady.ucsd.edu/faculty/directory/august/">Terrence August</a> and <a href="http://rady.ucsd.edu/faculty/directory/nijs/" target="\_blank">Vincent Nijs</a>. Developed by <a href="http://rady.ucsd.edu/faculty/directory/nijs/" target="\_blank">Vincent Nijs</a>. You can reach us at radiant@rady.ucsd.edu.

### How-to install Radiant

- Required: [R](https://github.com/mostly-harmless/radiant_miniCRAN/tree/gh-pages/R-3.1.2), version 3.1.2
- Required: A modern browser (e.g., Chrome, Safari, or Firefox)
- Recommended: [Rstudio](http://www.rstudio.com/products/rstudio/download/)

You can install the `Radiant` package and all package dependencies from the [radiant_miniCRAN](https://github.com/mostly-harmless/radiant_miniCRAN) repo (created using [miniCRAN](https://github.com/andrie/miniCRAN)). Open R(studio) and copy-and-paste the commands below.


```r
options(repos = c(XRAN = "http://mostly-harmless.github.io/radiant_miniCRAN/"))
install.packages("radiant")
```

Once all packages are installed use the commands below to start the app:

```r
library('radiant')
radiant()
```

To start the quant app use:

```r
library('radiant')
radiant('quant')
```

<!--
<iframe width="640" height="375" src="//www.youtube.com/embed/e02LFmNysoM" frameborder="0" allowfullscreen></iframe>
-->

### Starting and stopping Radiant

<iframe width="640" height="375" src="//www.youtube.com/embed/D71alRsGmBk" frameborder="0" allowfullscreen></iframe>

### Getting help

<iframe width="640" height="375" src="//www.youtube.com/embed/LFlCwapzAF0" frameborder="0" allowfullscreen></iframe>

### Getting data in and out of Radiant

<iframe width="640" height="375" src="//www.youtube.com/embed/6AE1Wa74cJI" frameborder="0" allowfullscreen></iframe>

### Generating predictions from regression

<iframe width="640" height="375" src="//www.youtube.com/embed/Xp1REGAewGU" frameborder="0" allowfullscreen></iframe>

### Creating a report

<iframe width="640" height="375" src="//www.youtube.com/embed/T_NQPfrWN-g" frameborder="0" allowfullscreen></iframe>

<!--
### Selecting variables for fast and efficient analysis
### View data in table form
### Visualize data
### Explore data
### Transform data
-->

### Radiant code

Version 0.1.1 (1/23/2015) Built using <a href="http://www.rstudio.com/shiny/" target="\_blank">Shiny</a> by <a href="http://www.rstudio.com/" target="\_blank">Rstudio</a>. Code available on <a href="https://github.com/mostly-harmless/radiant" target="_blank">GitHub</a>

### Package dependencies

```{r echo=FALSE, comment=NA}
	suppressMessages(
		devtools::source_url("https://raw.githubusercontent.com/mostly-harmless/radiant_miniCRAN/gh-pages/pkgs.R")
	)
```

`r sprintf("Package dependencies: %s", paste0(pkgs, collapse = ", "))`

<details>
<summary>Citing included packages</summary>
```{r echo=FALSE, comment=NA}
  suppressMessages(library(dplyr))
  for(i in c("radiant",pkgs)) citation(i) %>% print
```
</details>

### License

The Radiant package is licensed under the <a href="http://www.tldrlegal.com/l/AGPL3" target="\_blank">AGPLv3</a>. The help files are licensed under the creative commons attribution, non-commercial, share-alike license <a href="http://creativecommons.org/licenses/by-nc-sa/4.0/" target="\_blank">CC-NC-SA</a>.

As a summary, the AGPLv3 license requires, attribution, include copyright and license in copies of the software, state changes if you modify the code, and disclose all source code. Details are in the COPYING file.

