---
title: Radiant -- Business analytics using R and Shiny
---

***

```{r echo = FALSE}
 rv <- R.Version()
 rv <- paste(rv$major, rv$minor, sep = ".")
```

## How to install Radiant

Radiant is a platform-independent browser-based interface for business analytics in [R](http://www.r-project.org/), based on the [Shiny](http://www.rstudio.com/shiny/) package. Developed by <a href="http://rady.ucsd.edu/faculty/directory/nijs/" target="_blank">Vincent Nijs</a>. Please use the issue tracker on GitHub to suggest enhancements or report problems: <a href="https://github.com/radiant-rstats/radiant/issues" _target="_blank">https://github.com/radiant-rstats/radiant/issues</a>. For other questions and comments please use radiant@rady.ucsd.edu.


> **Note:** User profiles (or usernames or logins) containing non-ASCII characters will likely cause problems during installation. To address this issue please use a profile name (login) that contains ASCII (A-Z, a-z) letters only. For example, c:\\users\\myprofilename

#### 1. Install R for your system

For mac go to <a href="https://cran.rstudio.com/bin/macosx/" target="_blank">https://cran.rstudio.com/bin/macosx/</a>

For windows get the latest release from <a href="https://cran.rstudio.com/bin/windows/base/release.htm" target="_blank">https://cran.rstudio.com/bin/windows/base/release.htm</a>

> **Important:** Windows users **must** install R in directory C:\\R\\R-`r rv`

On Mac you can accept the default settings. On Windows the R-installer should create 2 shortcuts on your Desktop. Because we will be using Rstudio to start Radiant you can delete these shortcuts after completing step 6 below.

> To automate steps 2-5 open R and copy-and-paste the command below, press return, and accept all default settings during the install process:

```r
source("https://raw.githubusercontent.com/radiant-rstats/minicran/gh-pages/install.R")
```

For a step-by-step video tutorial see the `Install Radiant on Windows` or `Install Radiant on Mac` below:

**Install Radiant on Windows**

<iframe width="640" height="375" src="https://www.youtube.com/embed/efQM6WqrHG0" frameborder="0" allowfullscreen></iframe>

**Install Radiant on Mac**

<iframe width="640" height="375" src="https://www.youtube.com/embed/WheqHpobMZg" frameborder="0" allowfullscreen></iframe>

If you used the `source(...)` command shown above successfully you can now skip to step 6. Otherwise follow steps 2-5 below first.

#### 2. Install Rstudio

Get the latest release of Rstudio for your system from:

<a href="https://www.rstudio.com/products/rstudio/download/" target="_blank">https://www.rstudio.com/products/rstudio/download/</a>

Install Rstudio and accept all default settings. Make sure to put a shortcut to Rstudio on your Desktop or _pin_ it to the taskbar.

#### 3. Use a modern browser

For example, [Chrome](https://www.google.com/intl/en/chrome/browser/desktop/) or Safari. Internet Explorer (version 11 or higher) should work as well. Chrome, however, is the recommended browser. Most browser will, by default, save to the downloads folder. However, it is more convenient if the browser asks you where to save files. In Chrome got to _Preferences > Advanced preferences > Downloads_ and then check "Ask where to save each file before downloading".

#### 4. Install LaTex

To generate PDF reports in Radiant you will need LaTex installed. For Mac download and install <a href="http://tug.org/cgi-bin/mactex-download/MacTeX.pkg">MacTex</a>. For Windows download and install <a href="http://mirrors.ctan.org/systems/win32/miktex/setup/basic-miktex-2.9.6022-x64.exe">MikTex</a>.

#### 5. Install Radiant

To install Radiant open Rstudio and copy-and-paste the command below into the **Console** window on the bottom left of the application. Then press return. R(studio) will now install Radiant and several dependencies. This may take a few minutes depending on the speed of your internet connection.

> **Note:** On Windows you may need to start Rstudio by right-clicking on the desktop shortcut and choosing `run as administrator`.

```r
install.packages("radiant", repos = "https://radiant-rstats.github.io/minicran/", type = "binary")
```

> **Important:** If you use Windows and are asked where to install R-packages (i.e., "Would you like to use a personal library instead?") you most likely did **not** install R in directory C:\\R\\R-`r rv` as stated above. You should uninstall and reinstall R in the suggested directory before proceeding. If it already exists, you should also remove the Documents\\R directory.

#### 6. Starting Radiant

When you open Rstudio (version 0.99.900 or later) you can start and update Radiant through the `Addins` menu at the top of the screen. Note that when you first install Radiant you must use the install script or the `install.packages` command shown above.

When Radiant starts you will see data on diamond prices. To close the application click the <i title='Power off' class='fa fa-power-off'></i> icon in the navigation bar and then click `Stop`. The Radiant process will stop and the browser window will close (Chrome) or gray-out.

## Documentation

Documentation and tutorials for each of the apps are available at <http://radiant-rstats.github.io/docs/> and in the Radiant web interface (the <i title='Help' class='fa fa-edit'></i> icons on each page and the <i title='Help' class='fa fa-question-circle'></i> icon in the navigation bar).

Want more help getting started? Watch the tutorials on the [documentation site](http://radiant-rstats.github.io/docs/tutorials.html).

## Trouble shooting

Windows users may need to start R and Rstudio `as administrator`. On rare occasions R(studio) may complain that a package is not yet installed. If so, install the package mentioned using the command below but replace 'package-that-is-not-yet-installed' with the package name mentioned in the error message

```{r eval = FALSE}
install.packages("package-that-is-not-yet-installed", repos = "https://cran.rstudio.com", type = "binary")
```

## Reporting issues

Rady students can report any issues they might have with Radiant on Piazza. Otherwise, please use the GitHub issue tracker at <a href="https://github.com/radiant-rstats/radiant/issues" target="_blank">github.com/radiant-rstats/radiant/issues</a>.

