---
title: Radiant -- Business analytics using R and Shiny
---

***

## How to install Radiant

Radiant is a platform-independent browser-based interface for business analytics in [R](http://www.r-project.org/), based on the [Shiny](http://www.rstudio.com/shiny/) package. Developed by <a href="http://rady.ucsd.edu/faculty/directory/nijs/" target="\_blank">Vincent Nijs</a>. Please use the issue tracker on GitHub to suggest enhancements or report problems: <a href="https://github.com/vnijs/radiant/issues" _target="_blank">https://github.com/vnijs/radiant/issues</a>. For other questions and comments please use radiant@rady.ucsd.edu.

> **Note:** User profiles (or usernames or logins) containing non-ASCII characters will likely cause problems during installation. To address this issue please use a profile name (login) that contains ASCII (A-E, a-e) letters only. For example, c:\\users\\myprofilename

#### 1. Install R for your system

For mac go to <a href="https://cran.rstudio.com/bin/macosx/" target="_blank">https://cran.rstudio.com/bin/macosx/</a>

For windows you can get the latest release here: <a href="https://cran.rstudio.com/bin/windows/base/release.htm" target="_blank">https://cran.rstudio.com/bin/windows/base/release.htm</a>

> **Important:** Windows users must install R in directory C:\\R\\R-3.2.4

On Mac you can accept all the defaults. Installing R should create 2 shortcuts on your Desktop. Because we will be using Rstudio to start Radiant you can delete these shortcuts.

#### 2. Install Rstudio

Get the latest release of Rstudio for your system from:

<a href="https://www.rstudio.com/products/rstudio/download/" target="_blank">https://www.rstudio.com/products/rstudio/download/</a>

Install Rstudio and accept all default settings. Make sure to put a shortcut to Rstudio on your Desktop.

Although not required, I recommend that Windows users install <a href="https://cran.rstudio.com/bin/windows/Rtools/Rtools33.exe" target="_blank">Rtools</a>.

#### 3. Use a modern browser

For example, [Chrome](https://www.google.com/intl/en/chrome/browser/desktop/) or Safari. Internet Explorer (version 11 or higher) should work as well. Chrome, however, is the recommended browser.

#### 4. Install Radiant

To install Radiant open Rstudio and copy-and-paste the command below into the **Console** window on the bottom left of the application. Then press return. R(studio) will now install Radiant and several dependencies. This may take a few minutes depending on the speed of your internet connection.

> **Note:** On Windows you may need to start Rstudio by right-clicking on the desktop shortcut and choosing `run as administrator`.

```r
install.packages("radiant", repos = "http://vnijs.github.io/radiant_miniCRAN/", type = "binary")
```

> **Important:** If you use Windows and are asked where to install Radiant (i.e., "Would you like to use a personal library instead?") you did **not** install R in directory C:\\R\\R-3.2.4 as stated above. You will need to uninstall and reinstall R in the suggested directory before proceeding.

<!--
#### 5. Create a desktop launcher

To create icons on your Desktop to start and update Radiant, copy-and-paste (or type) ONE of the commands below into R (or Rstudio). For the Quantitative Analysis app use the `quant` command, for the Marketing Research app use the `marketing` command, and for the Customer Analytics app use the `analytics` command:

```r
## Choose one of the following three commands depending on the class you are in
radiant::launcher("quant")

radiant::launcher("marketing")

radiant::launcher("analytics")
```

After pasting the command press return. When asked if you want to create a short-cut type `y` and press return. A file called `radiant.bat` (windows) or `radiant.command` (mac) will be created that you can double-click to start Radiant in your default browser. The `launcher` command will also create a file called `update_radiant.bat` (windows) or `update_radiant.command` (mac) that you can double-click to update Radiant to the latest release.
-->


#### 5. Starting Radiant

When you open Rstudio (version 0.99.893 or later) by double-clicking the icon on your Desktop you can start and update Radiant through the `Addins` menu at the top of the screen. Note that when you first install Radiant you must use the `install.packages` command mentioned above. For Quantitative Analysis or Business Analytics click `Radiant - Quant`, for Marketing Research click `Radiant - Marketing`, and for Customer Analytics click `Radiant - Analytics`:

Alternatively, you can start Radiant from R(studio) using one of the commands below. For Quantitative Analysis or Business Analytics use `quant`, for Marketing Research use `marketing`, and for Customer Analytics use `analytics`:

```r
library(radiant)

## Choose ONE of the following three commands depending on the class you are in
radiant("quant")

radiant("marketing")

radiant("analytics")
```

When Radiant starts you will see data on diamond prices. To close the application click the <i title='Power off' class='fa fa-power-off'></i> icon in the navigation bar and then click `Stop`. The Radiant process will stop and the browser window will close (Chrome) or gray-out. If you get stuck, take a look at the `Installing Radiant` video:

<iframe width="640" height="375" src="https://www.youtube.com/embed/NEPSFiHH_dw" frameborder="0" allowfullscreen></iframe>

## Documentation

Documentation and tutorials for each of the apps are available at <http://vnijs.github.io/radiant/> and in the Radiant web interface (the <i title='Help' class='fa fa-edit'></i> icons on each page and the <i title='Help' class='fa fa-question-circle'></i> icon in the navigation bar).

Want more help getting started? Watch the tutorials on the [documentation site](http://vnijs.github.io/radiant/tutorials.html).

## Trouble shooting

As mentioned above, Windows users may need to start Rstudio) by right-clicking on the Rstudio desktop shortcut and choosing `run as administrator`.

On Windows, if you see a message such as "Warning: unable to move temporary installation 'C:\Users\yourname\Documents\R\win-library\3.2\file54ad976f6\shinyAce' to 'C:\Users\yourname\Documents\R\win-library\3.2\shinyAce'"
you will need to reinstall R into C:\\R\\R-3.2.4 as mentioned above. You should also remove the directory Documents\\R from your computer

On rare occasions R(studio) may complain that a package is not yet installed. If so, install the package mentioned using the command below but replace 'package-that-is-not-yet-installed' with the package name mentioned in the error message

```{r eval = FALSE}
install.packages("package-that-is-not-yet-installed", repos = "http://vnijs.github.io/radiant_miniCRAN/", type = "binary")
```

If R(studio) complains about not being able to delete a package or directory please copy-and-paste the commands below into R (or Rstudio) and press return. Then double-click the `update_radiant` icon on your desktop again. If the update is successful (i.e., no error messages) try double clicking the `radiant` icon on your desktop again.

```{r eval = FALSE}
remove.packages("Rcpp", lib = .libPaths())
remove.packages("dplyr", lib = .libPaths())
```

## Reporting issues

Rady students can report any issues they might have with Radiant on the class Piazza site.

Otherwise, please use the GitHub issue tracker at <a href="https://github.com/vnijs/radiant/issues" target="_blank">github.com/vnijs/radiant/issues</a> if you have any problems with Radiant.

